### 2010-02-25 trunk/deliverables/D2_2_Ontology/properties.tex
pretty much done with the very last revisions. more figures, better text, ontology code revised.
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@602 d8b0c59b-6544-0410-94d9-83a5658a058e

@@

\subsubsection*{Property: \texttt{fgo:hasIdActionTo}}
\label{subs:hasIdActionTo}
\textcolor{white}{\textbf{label}} & has id action to \\ \hline
\textcolor{white}{\textbf{description}} & action id of the `to' point of the pipe or trigger. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Pipe}}{subs:Pipe}, \htmlref{\texttt{fgo:Trigger}}{subs:Trigger} \\ \hline
\subsubsection*{Property: \texttt{fgo:hasIdBBFrom}}
\label{subs:hasIdBBFrom}
\textcolor{white}{\textbf{label}} & has id building block from \\ \hline
\textcolor{white}{\textbf{description}} & building block id of the `from' point of the pipe or trigger. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Pipe}}{subs:Pipe}, \htmlref{\texttt{fgo:Trigger}}{subs:Trigger} \\ \hline
\subsubsection*{Property: \texttt{fgo:hasIdBBTo}}
\label{subs:hasIdBBTo}
\textcolor{white}{\textbf{label}} & has id building block to \\ \hline
\textcolor{white}{\textbf{description}} & building block id of the `to' point of the pipe or trigger. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Pipe}}{subs:Pipe}, \htmlref{\texttt{fgo:Trigger}}{subs:Trigger} \\ \hline
\subsubsection*{Property: \texttt{fgo:hasIdConditionFrom}}
\label{subs:hasIdConditionFrom}
\textcolor{white}{\textbf{label}} & has id condition from \\ \hline
\textcolor{white}{\textbf{description}} & condition id of the `from' point of the pipe. \\ \hline
\subsubsection*{Property: \texttt{fgo:hasIdConditionTo}}
\label{subs:hasIdConditionTo}
\textcolor{white}{\textbf{label}} & has id condition to \\ \hline
\textcolor{white}{\textbf{description}} & condition id of the `to' point of the pipe. \\ \hline

@@

\subsubsection*{Property: \texttt{fgo:hasNameFrom}}
\label{subs:hasNameFrom}
\textcolor{white}{\textbf{label}} & has name from \\ \hline
\textcolor{white}{\textbf{description}} & name of the trigger. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Trigger}}{subs:Trigger} \\ \hline

@@

@@

@@

\subsubsection*{Property: \texttt{fgo:hasUse}}
\label{subs:hasUse}
\textcolor{white}{\textbf{label}} & has use string \\ \hline
pre/postcondition. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Action}}{subs:Action} \\ \hline

@@

>>>>

\subsubsection*{Property: \texttt{fgo:from}}
\label{subs:from}
\textcolor{white}{\textbf{label}} & from \\ \hline
\textcolor{white}{\textbf{description}} & This property defines the starting point of a pipe within a screen. \\ \hline

@@

@@

@@

\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Condition}}{subs:Condition} \\ \hline

@@

\textcolor{white}{\textbf{range}} & \texttt{xsd:Condition} \\ \hline

@@

@@

\subsubsection*{Property: \texttt{fgo:to}}
\label{subs:to}
\textcolor{white}{\textbf{label}} & to \\ \hline
\textcolor{white}{\textbf{description}} & This property defines the end point of a pipe within a screen. \\ \hline
\subsubsection*{Property: \texttt{fgo:uses}}
\label{subs:uses}
\textcolor{white}{\textbf{label}} & uses \\ \hline
pre- or post-condition. \\ \hline
